Energy and the CES production function

### 2015-08-26 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Changing figure sizes.

<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=7.5, fig.height=2.8, fig.cap="Ternary graph of output elasticities~($\\alpha$). This version shows all Unadjusted and Quality-adjusted points on the same graph. Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
p <- triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( nest = plyr::mapvalues(nest, 
                                   from=c("kle", "lek", "ekl"), 
                                   to=c("(kl)e", "(le)k", "(ek)l")),
            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor
            ), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model,
      color = Inputs)
  ) +
  labs(color = "Factors of production") +
  facet_grid(. ~ Country)
  model_points_style(p)
@

<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=7.5, fig.height=5, fig.cap="Ternary graph of output elasticities~($\\alpha$). This version splits the Unadjusted and Quality-adjusted values on their own graphs. This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
p <- triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( nest = plyr::mapvalues(nest, 
                                   from=c("kle", "lek", "ekl"), 
                                   to=c("(kl)e", "(le)k", "(ek)l")),
            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model
      # color = Inputs
      )
  ) +
  facet_grid(Inputs ~ Country)

@@

<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, fig.cap="Elasticities of substitution~($\\sigma$).">>=
breaks_labels = c(0.01, 0.1, 1, 10, 100)
p <- 
ggplot(
  AllCoeffs %>% 
    gather(type, value, matches("sigma")) %>% 
    filter(!is.na(value)) %>% 
    filter(! type %in% c("sigma", "sigma_1")) %>%
    mutate(nest = plyr::mapvalues(nest, 
                                  from=c("kle", "lek", "ekl"), 
                                  to=c("(kl)e", "(le)k", "(ek)l")),
           type = relevelFactor(type, c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")),
           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
           Inputs = flavor
           )
  ) + 
  geom_point(aes(x=value, y=type, 
                 shape = Model, fill=Model, size=Model,
                 color=Inputs
                 )
                 # position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( type ~ Country, scales = "free_y" ) + 
  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  scale_y_discrete(labels = c(
    sigma_12 = expression(sigma[kl]),
    sigma_23 = expression(sigma[le]),
    sigma_13 = expression(sigma[ek]),
    sigma_12_3 = expression(sigma["(kl)"*e]),
    sigma_23_1 = expression(sigma["(le)"*k]),
    sigma_13_2 = expression(sigma["(ek)"*l]))
    ) +
  ylab("") +
  labs(color = "Factors of production") +
  xy_theme() +
  theme(
    legend.position="top",
    strip.text.y = element_blank())

@@

<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
breaks_labels = c(0.01, 0.1, 1, 10, 100)
p <- 
  ggplot(
    AllCoeffs %>% 
      gather(type, value, matches("sigma")) %>% 
      filter(!is.na(value)) %>% 
      filter(! type %in% c("sigma", "sigma_1")) %>%
      mutate(nest = plyr::mapvalues(nest, 
                                    from=c("kle", "lek", "ekl"), 
                                    to=c("(kl)e", "(le)k", "(ek)l")),
             Model = interaction(nest, CSP, sep = " ", drop=TRUE),
             Inputs = flavor,
             type = relevelFactor(type, rev(c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")))
             )
    ) + 
  geom_point(aes(x=value, 
                 y=type, 
                 shape = Model, 
                 fill=Model, 
                 size=Model
                 )
             ) + 
  facet_grid( Inputs ~ Country) + 
  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  ylab("") +
  scale_y_discrete(labels = c(
    sigma_12 = expression(sigma[kl]),
    sigma_23 = expression(sigma[le]),
    sigma_13 = expression(sigma[ek]),
    sigma_12_3 = expression(sigma["(kl)"*e]),
    sigma_23_1 = expression(sigma["(le)"*k]),
    sigma_13_2 = expression(sigma["(ek)"*l]))
    ) +
  xy_theme()

>>>>

<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=2.3, fig.cap="Ternary graph of output elasticities~($\\alpha$). This version shows all Unadjusted and Quality-adjusted points on the same graph. Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
p <- triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( nest = plyr::mapvalues(nest, 
                                   from=c("kle", "lek", "ekl"), 
                                   to=c("(kl)e", "(le)k", "(ek)l")),
            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor
            ), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model,
      color = Inputs)
  ) +
  labs(color = "Factors of production") +
  facet_grid(. ~ Country)
  model_points_style(p)
@

<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=4.1, fig.cap="Ternary graph of output elasticities~($\\alpha$). This version splits the Unadjusted and Quality-adjusted values on their own graphs. This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
p <- triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( nest = plyr::mapvalues(nest, 
                                   from=c("kle", "lek", "ekl"), 
                                   to=c("(kl)e", "(le)k", "(ek)l")),
            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model
      # color = Inputs
      )
  ) +
  facet_grid(Inputs ~ Country)

@@

<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$).">>=
breaks_labels = c(0.01, 0.1, 1, 10, 100)
p <- 
ggplot(
  AllCoeffs %>% 
    gather(type, value, matches("sigma")) %>% 
    filter(!is.na(value)) %>% 
    filter(! type %in% c("sigma", "sigma_1")) %>%
    mutate(nest = plyr::mapvalues(nest, 
                                  from=c("kle", "lek", "ekl"), 
                                  to=c("(kl)e", "(le)k", "(ek)l")),
           type = relevelFactor(type, c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")),
           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
           Inputs = flavor
           )
  ) + 
  geom_point(aes(x=value, y=type, 
                 shape = Model, fill=Model, size=Model,
                 color=Inputs
                 )
                 # position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( type ~ Country, scales = "free_y" ) + 
  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  scale_y_discrete(labels = c(
    sigma_12 = expression(sigma[kl]),
    sigma_23 = expression(sigma[le]),
    sigma_13 = expression(sigma[ek]),
    sigma_12_3 = expression(sigma["(kl)"*e]),
    sigma_23_1 = expression(sigma["(le)"*k]),
    sigma_13_2 = expression(sigma["(ek)"*l]))
    ) +
  ylab("") +
  labs(color = "Factors of production") +
  xy_theme() +
  theme(
    legend.position="top",
    strip.text.y = element_blank(),
    axis.text.y = element_text(size=12)
    )

@@

<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
breaks_labels = c(0.01, 0.1, 1, 10, 100)
p <- 
  ggplot(
    AllCoeffs %>% 
      gather(type, value, matches("sigma")) %>% 
      filter(!is.na(value)) %>% 
      filter(! type %in% c("sigma", "sigma_1")) %>%
      mutate(nest = plyr::mapvalues(nest, 
                                    from=c("kle", "lek", "ekl"), 
                                    to=c("(kl)e", "(le)k", "(ek)l")),
             Model = interaction(nest, CSP, sep = " ", drop=TRUE),
             Inputs = flavor,
             type = relevelFactor(type, rev(c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")))
             )
    ) + 
  geom_point(aes(x=value, 
                 y=type, 
                 shape = Model, 
                 fill=Model, 
                 size=Model
                 )
             ) + 
  facet_grid( Inputs ~ Country) + 
  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  ylab("") +
  scale_y_discrete(labels = c(
    sigma_12 = expression(sigma[kl]),
    sigma_23 = expression(sigma[le]),
    sigma_13 = expression(sigma[ek]),
    sigma_12_3 = expression(sigma["(kl)"*e]),
    sigma_23_1 = expression(sigma["(le)"*k]),
    sigma_13_2 = expression(sigma["(ek)"*l]))
    ) +
  xy_theme() +
  theme(axis.text.y = element_text(size=12))
